The \dealii{} Library, Version 9.4

### 2022-05-26 9.4/paper.tex
More small improvements.

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii{} release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
%  \item \texttt{AffineConstraints::make\_consistent\_in\_parallel()} allows
%  to make constraints consistent in parallel.
  \item The \texttt{DataOutResample} class does not output a numerical solution 
  on the cells of the original triangulation, but interpolates the result 
  onto a second triangulation (which can be completely unrelated). 
  By using this class, one can output the result obtained on an 
  unstructured mesh on a structured one, which might be a more
  memory-efficient storage format, or one can create a slice in 3D.
  \item The new function \texttt{find\_point\_owner\_rank()} of \texttt{parallel::distributed::Triangulation} allows to find the MPI
  rank of the subdomain of a distributed mesh that contains a given point.
  It is communication-free and leverages the functionality of p4est (>v.2.2).
  Its algorithm is described in \cite{burstedde2020parallel}. Based on the information obtained,
  communication pattern in \texttt{Utilties::MPI::RemotePointEvaluation} can be set up efficiently. Furthermore, this function could be used in the future to allow
  particle simulations where particle movement is not
  limited by CFL conditions, as done in \cite{mirzadeh2016parallel}.
  \item The new function
  \texttt{GridGenerator::pipe\_junction}
  generates a triangulation of three cone-shaped pipes that cross at a bifurcation point in any possible configuration.
  A manifold description will be applied to the boundary, which can be extended into the volume via transfinite interpolation \cite{Gordon82} using the \texttt{TransfiniteInterpolationManifold} class \cite{dealII90}.
  \todo[inline]{[MF] If desired, I can extend this part into its own
    section of the main chapter. With figures, this would probably
    occupy about 3/4 of a page.}
  \item \todo[inline]{Add something about the FEInterfaceValues improvements.}
\end{itemize}
%
The changelog lists more than 150 other features and bugfixes.

@@

\dealii{} can interface with many other libraries:
\begin{multicols}{3}
  \begin{itemize}
    \item ADOL-C \cite{Griewank1996a,adol-c}
    \item ArborX \cite{lebrun2020arborx}
    \item ARPACK \cite{arpack}
    \item Assimp \cite{assimp}
    \item BLAS and LAPACK \cite{lapack}
    \item cuSOLVER \cite{cusolver}
    \item cuSPARSE \cite{cusparse}
    \item Gmsh \cite{geuzaine2009gmsh}
    \item GSL \cite{gsl2016}
    \item Ginkgo \cite{ginkgo-web-page}
    \item HDF5 \cite{hdf5}
    \item METIS \cite{karypis1998fast}
    \item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
    \item muparser \cite{muparser-web-page}
    \item OpenCASCADE \cite{opencascade-web-page}
    \item p4est \cite{p4est}
    \item PETSc \cite{petsc-user-ref,petsc-web-page}
    \item ROL \cite{ridzal2014rapid}
    \item ScaLAPACK \cite{slug}
    \item SLEPc \cite{Hernandez:2005:SSF}
    \item SUNDIALS \cite{sundials}
    \item SymEngine \cite{symengine-web-page}
    \item TBB \cite{Rei07}
    \item Trilinos \cite{trilinos,trilinos-web-page}
    \item UMFPACK \cite{umfpack}
  \end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use
interfaces to these libraries.

The two previous releases of \dealii{} can be cited as
\cite{dealII91,dealII92}.

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.4: updated 23/04/2022 PM
Pasquale	Africa,
Tyler	Anderson,
Francesco	Andreuzzi,
Mathias	Anselmann,
Maximilian	Bergbauer,
Bruno	Blais,
Till	Budde,
Fabian	Castelli,
Praveen	Chandrashekar,
Cu	Cui,
Ivo	Dravins,
Niklas	Fehn,
Johannes	Friedlein,
Sebastian	Fuchs,
Rene	Gassmoeller,
Nicola	Giuliani,
Alexander	Grayver,
Diane	Guignard,
Jake	Harmon,
Sean	Ingimarson,
Pengfei	Jia,
Sebastian	Kinnewig,
Simon	Konrad,
Katharina	Kormann,
Paras	Kumar,
Wenyu	Lei,
Alberto F.	Martin,
Nils	Much,
Lucas	Myers,
Justin	O'Connor,
Judith	Pauen,
Vachan	Potluri,
Raghunandan	Pratoori,
Sebastian	Proell,
Ce	Qin,
Reza	Rastak,
Jose E.	Roman,
Raphael	Schoof,
Magdalena	Schreter,
Konrad	Simon,
Simon	Sticko,
Bruno	Turcksin,
Kuljit S.	Virk,
Michał	Wichrowski,
Niklas Wik,
Jiaqi	Zhang.

@@

>>>>

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii{} release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
%  \item \texttt{AffineConstraints::make\_consistent\_in\_parallel()} allows
%  to make constraints consistent in parallel.
  \item The \texttt{DataOutResample} class does not output a numerical solution 
  on the cells of the original triangulation, but interpolates the result 
  onto a second triangulation (which can be completely unrelated). 
  By using this class, one can output the result obtained on an 
  unstructured mesh on a structured one, which might be a more
  memory-efficient storage format, or one can create a slice in 3D.
  \item The new function \texttt{find\_point\_owner\_rank()} of \texttt{parallel::distributed::Triangulation} allows to find the MPI
  rank of the subdomain of a distributed mesh that contains a given point.
  It is communication-free and leverages the functionality of p4est (>v.2.2).
  Its algorithm is described in \cite{burstedde2020parallel}. Based on the information obtained,
  communication pattern in \texttt{Utilties::MPI::RemotePointEvaluation} can be set up efficiently. Furthermore, this function could be used in the future to allow
  particle simulations where particle movement is not
  limited by CFL conditions, as done in \cite{mirzadeh2016parallel}.
  \item The new function
  \texttt{GridGenerator::pipe\_junction}
  generates a triangulation of three cone-shaped pipes that cross at a bifurcation point in any possible configuration.
  A manifold description will be applied to the boundary, which can be extended into the volume via transfinite interpolation \cite{Gordon82} using the \texttt{TransfiniteInterpolationManifold} class \cite{dealII90}.
  \todo[inline]{[MF] If desired, I can extend this part into its own
    section of the main chapter. With figures, this would probably
    occupy about 3/4 of a page.}
  \item \todo[inline]{Add something about the FEInterfaceValues improvements.}
\end{itemize}
%
The changelog lists more than 175 other features and bugfixes.
\todo{This number is up to date.}

@@

\dealii{} can interface with many other libraries:
\todo[inline]{Need to update, in particular add CGAL.}
\begin{multicols}{3}
  \begin{itemize}
    \item ADOL-C \cite{Griewank1996a,adol-c}
    \item ArborX \cite{lebrun2020arborx}
    \item ARPACK \cite{arpack}
    \item Assimp \cite{assimp}
    \item BLAS and LAPACK \cite{lapack}
    \item cuSOLVER \cite{cusolver}
    \item cuSPARSE \cite{cusparse}
    \item Gmsh \cite{geuzaine2009gmsh}
    \item GSL \cite{gsl2016}
    \item Ginkgo \cite{ginkgo-web-page}
    \item HDF5 \cite{hdf5}
    \item METIS \cite{karypis1998fast}
    \item MUMPS \cite{ADE00,MUMPS:1,MUMPS:2,mumps-web-page}
    \item muparser \cite{muparser-web-page}
    \item OpenCASCADE \cite{opencascade-web-page}
    \item p4est \cite{p4est}
    \item PETSc \cite{petsc-user-ref,petsc-web-page}
    \item ROL \cite{ridzal2014rapid}
    \item ScaLAPACK \cite{slug}
    \item SLEPc \cite{Hernandez:2005:SSF}
    \item SUNDIALS \cite{sundials}
    \item SymEngine \cite{symengine-web-page}
    \item TBB \cite{Rei07}
    \item Trilinos \cite{trilinos,trilinos-web-page}
    \item UMFPACK \cite{umfpack}
  \end{itemize}
\end{multicols}
Please consider citing the appropriate references if you use
interfaces to these libraries.

The two previous releases of \dealii{} can be cited as
\cite{dealII92,dealII93}.

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
\todo[inline]{updated 23/04/2022 PM. We should probably make sure that
  nobody else came after that and before the release.}
Pasquale	Africa,
Tyler	Anderson,
Francesco	Andreuzzi,
Mathias	Anselmann,
Maximilian	Bergbauer,
Bruno	Blais,
Till	Budde,
Fabian	Castelli,
Praveen	Chandrashekar,
Cu	Cui,
Ivo	Dravins,
Niklas	Fehn,
Johannes	Friedlein,
Sebastian	Fuchs,
Rene	Gassmoeller,
Nicola	Giuliani,
Alexander	Grayver,
Diane	Guignard,
Jake	Harmon,
Sean	Ingimarson,
Pengfei	Jia,
Sebastian	Kinnewig,
Simon	Konrad,
Katharina	Kormann,
Paras	Kumar,
Wenyu	Lei,
Alberto F.	Martin,
Nils	Much,
Lucas	Myers,
Justin	O'Connor,
Judith	Pauen,
Vachan	Potluri,
Raghunandan	Pratoori,
Sebastian	Proell,
Ce	Qin,
Reza	Rastak,
Jose E.	Roman,
Raphael	Schoof,
Magdalena	Schreter,
Konrad	Simon,
Simon	Sticko,
Bruno	Turcksin,
Kuljit S.	Virk,
Michał	Wichrowski,
Niklas Wik,
Jiaqi	Zhang.

@@

\todo[inline]{Update. In particular make sure that we remove those who
  are not authors on this paper.}
